Untitled

### 2024-11-25 code/manuscript_altanalysis.Rmd
submitted figures

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise(mean.nas(Closed), n())

@@

strat.temp <- coeffs.did.strat
strat.temp[3,] <- strat.temp[3,] / 1000
strat.temp[23,] <- strat.temp[23,] / 100
strat.temp[18,] <- strat.temp[18,] / 100

@@

strat.temp$Outcome <- rep(c("Composite Quality of Care, %", "Total Patients Served, No.","Financial resilience,\nAltman’s Z Score", "Patient-to-Staff Ratio","Average prevalence of\nselect chronic conditions, %","Intensity", "Medicaid, %","Uninsured, %","CostPerPat","Quick Ratio, %","Months of Cash Available", "Revenue-to-Expenses, Ratio %","Liabilities-to-Assets, Ratio %","Staff, No.","Closure, Acquisition or\nloss of FQHC status, %"), 2)

p <- strat.temp  %>% 
  filter(Outcome %notin% c("Intensity","CostPerPat")) %>%

@@

@@

>>>>

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed, Complexity) %>% 
  summarise(mean.nas(Closed), n(), mean.nas(Complexity))

@@

strat.temp <- coeffs.did.strat
strat.temp[3,] <- strat.temp[3,] / 1000
strat.temp[23,] <- strat.temp[23,] / 10
strat.temp[18,] <- strat.temp[18,] / 100

#strat.temp[12,] <- strat.temp[12,] / 5.5 * 100

strat.temp <- coeffs.did.strat

strat.temp <- (strat.temp/(df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp:Closed) %>% 
  summarise_all(mean.nas) %>% 
  filter(Post == 0 & Treat == "Treated") %>% 
  t())[-c(2)] %>% 
  as.numeric() * 100)[-24,] %>% 
  rbind(coeffs.did.strat[24,])

@@

strat.temp$Outcome <- rep(c("Composite Quality of Care", "Total Patients Served","Financial resilience,\nAltman’s Z Score", "Patient-to-Staff Ratio","Average prevalence of\nselect chronic conditions","Intensity", "Medicaid","Uninsured","CostPerPat","Quick Ratio","Months of Cash Available", "Revenue-to-Expenses","Liabilities-to-Assets","Staff","Closure, Acquisition or\nloss of FQHC status"), 2)

p <- strat.temp  %>% 
  filter(Outcome %notin% c("Intensity","CostPerPat","Months of Cash Available")) %>%

@@

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("Effect Estimates (% change)") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

@@

colnames(df.temptemp)[17:39]
